Real-time Attention Assessment for Social Robots

### 2015-08-29 paper.tex
Updated title
Rewritten abstract

\title{On-line Vision-based Engagement Assessment for Interactive Robots}
\author{Fernando Garcia \qquad Séverin Lemaignan \qquad Alexis Jacq \qquad Pierre Dillenbourg\\Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)\\École Polytechnique Fédérale de Lausanne (EPFL)}

\maketitle
\begin{abstract}
In long term interactions between humans and robots, it is necessary that the agent exhibits some sort of social intelligence to be able to engage the human providing the appropriate response to specific face-to-face situations. In a educational context, this feature becomes a must due to the fact that engagement plays a relevant role in the learning process. Therefore, maximizing the interaction time at a high engagement level provides learning benefits. In this work, a visual focus of attention based on head pose estimation using a camera is proposed to be able to monitor and assess the quality of the interaction. We want to show a practical approach to evaluate the engagement that arises from the interaction reporting several experiences in the field, with the robot Nao and discussing the experimental results.
\end{abstract}

@@

\keywords{Human-Robot Interaction; Social Robotics; Children.}

>>>>

\title{Real-time Attention Assessment for Social Robots}
\author{Fernando Garcia \qquad Séverin Lemaignan \qquad Alexis Jacq \qquad Pierre Dillenbourg\\Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)\\École Polytechnique Fédérale de Lausanne (EPFL)}

\maketitle
\begin{abstract}
Successfully sustaining face-to-face interaction between humans and robots mandates fine perception of each other attentional focus. Along this line, we present a novel technique to assess the visual focus of attention (VFOA) based on accurate, real-time head pose estimation with monocular camera. The software is fully open-source and can readily be adopted on a wide range of social robots. We propose an in-depth evaluation of the technique, using manual video annotations as ground truth, and show that our system reaches high level of accuracy in a real-world face-to-face interaction scenario. We finally show how to derive a metric of engagement from the monitoring of the VFOA, allowing the robot to account and react to the user's changing engagement in real-time.
\end{abstract}

@@

\keywords{Human-Robot Interaction; Social Robotics; Attention Assessment; Engagement; Computer Vision.}
